# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data
```{r tidy=FALSE}
healthData<-read.csv("activity.csv") 
dailyHeathData<-aggregate(steps~date, healthData, sum)
intervalHealthData<-aggregate(steps~interval, healthData, mean)
```
## What is mean total number of steps taken per day?
```{r tidy=FALSE}
hist(dailyHeathData$steps, breaks=16)
mean(dailyHeathData$steps)
median(dailyHeathData$steps)
```

## What is the average daily activity pattern?
```{r tidy=FALSE}
plot(intervalHealthData$interval, intervalHealthData$steps, type='l')
intervalHealthData[intervalHealthData$steps==max(intervalHealthData$steps),]
```


## Imputing missing values
```{r tidy=FALSE}
nrow(healthData[!is.na(healthData$steps),])
```
We now make a copy of the original data set to replace the NAs with the means for every interval(taken across all days), that we had previously calculated.
```{r tidy=FALSE}
assign("interpolatedHealthData", healthData)
for (i in 1:nrow(interpolatedHealthData)) {
  if(is.na(interpolatedHealthData[i, "steps"]))
    interpolatedHealthData[i, "steps"]<-intervalHealthData[intervalHealthData$interval==interpolatedHealthData[i, "interval"],]$steps
}
```

The new graph looks something like this
```{r tidy=FALSE}
interpolatedDailyHeathData<-aggregate(steps~date, interpolatedHealthData, sum)
hist(interpolatedDailyHeathData$steps, breaks=16)
mean(interpolatedDailyHeathData$steps)
median(interpolatedDailyHeathData$steps)
```
As expected, the mean remains unchanged, but the median becomes the same as the mean.

## Are there differences in activity patterns between weekdays and weekends?
```{r tidy=FALSE}
weekdaysData<-weekdays(as.Date(healthData$date))
interpolatedHealthData["weekday"]<-weekdaysData
weekdaysHealthData<-interpolatedHealthData[!(interpolatedHealthData$weekday %in% c('Saturday','Sunday')),]
weekendsHealthData<-interpolatedHealthData[(interpolatedHealthData$weekday %in% c('Saturday','Sunday')),]
weekdaysIntervalData<-aggregate(steps~interval, weekdaysHealthData, mean)
weekendsIntervalData<-aggregate(steps~interval, weekendsHealthData, mean)

plot(weekdaysIntervalData$interval, weekdaysIntervalData$steps, type='l')
plot(weekendsIntervalData$interval, weekendsIntervalData$steps, type='l')
```